### 2021-07-21 paper/paper.tex
add draft of PID figures for Euler

@@

\begin{abstract}
TODO: abstract %TODO
\end{abstract}

@@

TODO %TODO
\begin{itemize}
  \item Basic design of Trixi.jl and its capabilities
  \item PID comparison of Fluxo and Trixi.jl
  \item Discussion on Julia for numerical simulation science
  \item Prepare repro repo including scripts for Trixi.jl and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward}
\end{itemize}

@@

>>>>

% Use multiple images in a single environment
\usepackage{subcaption}

% Plotting in tikz images
\usepackage{pgfplots}
% Silence warnings
\pgfplotsset{compat=1.16}
% Allow external generation of images to speed up compilation
% \usetikzlibrary{external}
% \tikzexternalize[prefix=../figures/tikz/]

@@

\begin{abstract}
TODO: abstract (at most 600 characters, written in plain English with no symbol
nor formula + references etc.) %TODO
\end{abstract}

@@

TODO %TODO
\begin{itemize}
  \item Basic design of Trixi.jl and its capabilities
  \item PID comparison of Fluxo and Trixi.jl
  \item Discussion on Julia for numerical simulation science
  \item Prepare repro repo including scripts for Trixi.jl and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward}
  \item Change title to something like ``Adaptive high-order numerical simulations
  of hyperbolic PDEs with Trixi.jl. A case study of Julia for scientific computing''?
\end{itemize}

\section{Performance comparison with FLUXO}

FLUXO\footnote{\url{https://gitlab.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection diffusion equations. It also
implements the same kind of modern DG methods based on flux differencing
to achieve entropy conservation/dissipation or kinetic energy preservation.
Thus, both Trixi.jl and FLUXO share a common set of features, enabling a reasonable
comparison of their performance.

Here, we compare the serial performance of Trixi.jl and FLUXO when solving a
hyperbolic PDE in three space dimensions on curvilinear hex meshes.

TODO: Andrew, please describe the setups that you used.

\begin{figure}
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (seconds)},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.2e-6,
          grid=major,
        ]
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak.dat};
        %   \addlegendentry{\texttt{TreeMesh} (Trixi.jl)}
        \addplot[blue, mark=*, solid]
          table [x index=0, y index=3]{../data/pids_euler_weak.dat};
          \addlegendentry{\footnotesize FLUXO}
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak.dat};
          % \addlegendentry{\texttt{StructuredMesh} (Trixi.jl)}
          \addlegendentry{\footnotesize Trixi.jl}
        \node at (axis cs:13,3.5e-7) {Weak form};

        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha.dat};
        \addplot[blue, mark=*, dashed]
          table [x index=0, y index=3]{../data/pids_euler_ranocha.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha.dat};
        \node [rotate=23] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:7.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          ymin=0.0,
          ymax=1.1,
          ytick={0,0.25,0.5,0.75,1},
          grid=major,
        ]
        % \addplot[blue, mark=square*, solid]
        %   table [x index=0, y index=1]{../data/pids_euler_weak_relative.dat};
        \addplot[red, mark=diamond*, solid]
          table [x index=0, y index=2]{../data/pids_euler_weak_relative.dat};
        \addplot[blue, mark=*, solid]
          table [x index=0, y index=3]{../data/pids_euler_weak_relative.dat};

        % \addplot[blue, mark=square*, dashed]
        %   table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed]
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
        \addplot[blue, mark=*, dashed]
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};

        % \node at (axis cs:10,0.6) {Will be improved soon};
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
\end{figure}

@@

Full paper: 5--10 pages.
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}
